The hidden manifold distance for functional manifold data

### 2019-06-24 index.Rmd
update cluster_results

## Performance metrics
We introduce a new metric for assessing the quality of a pairwise geodesic distance estimator. This is the ROC curve with $\epsilon$ on the $x$-axis and degree to which near-$\epsilon$ isometry holds, i.e.\ the percentage of estimated pairwise distances between $1-\epsilon$ and $1+\epsilon$ of the truth pairwise distance.

@@

Suppose we take scenario 1 where the geodesic distance coincides with the $L_2$ distance. Then what is the cost of employing our distance estimator compared to smoothing the data and doing numerical integration to find the $L_2$ distance.

@@

* Wheat, rainfall and phoneme in Aurore's paper "Achieving near-perfect classification for functional data"
* Berkeley growth curves in Chen et. al 2014, Biometrics.
* Tecator and phoneme in Mahalanobis technometrics paper.

Datasets used in functional manifold papers
* Berkeley growth, yeast cell cycle gene expression in Chen and Muller
* Tecator in Lin and Yao's contamination paper
* Berkeley growth, gait cycle in Jean-Michel Loubes' robust isomap paper

>>>>

## Performance metrics
We describe three different metrics we use to assess the quality of a pairwise geodesic distance estimator. This is the ROC curve with $\epsilon$ on the $x$-axis and degree to which near-$\epsilon$ isometry holds, i.e.\ the percentage of estimated pairwise distances between $1-\epsilon$ and $1+\epsilon$ of the truth pairwise distance.

@@

Suppose we take scenario 1 where the geodesic distance coincides with the $L_2$ distance. Then what is the cost of employing our distance estimator compared to smoothing the data and doing numerical integration to find the $L_2$ distance?

@@

* Wheat, rainfall and phoneme in Aurore's paper "Achieving near-perfect classification for functional data"
* Berkeley growth curves in Chen et. al 2014, Biometrics.
* Tecator and phoneme in Mahalanobis technometrics paper.
* yeast cell cycle gene expression (can't find this publicly) in Leng and Muller's "Classification using functional data analysis for temporal gene expression data"

Datasets used in functional manifold papers
* Berkeley growth, yeast cell cycle gene expression (can't find this publicly) in Chen and Muller
* Tecator in Lin and Yao's contamination paper
* Berkeley growth, gait cycle in Jean-Michel Loubes' robust isomap paper
